Supporting Information:\\ NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PE and PG lipids

### 2021-04-19 manuscriptPGPEsuppl.tex
Updates from Overleaf

\begin{figure}[]
%  \centering
  \includegraphics[width=\textwidth]{./Figs/POPG_SI.pdf}
  \caption{\label{POPGspectra}
    Solid-state NMR spectroscopy for determining the C--H bond order parameters, $S_{\rm{CH}}$, in the POPG headgroup and glycerol backbone. (A) Chemical structure of POPG showing the labels used to identify different carbons.
    (B) Refocused INEPT $^{13}$C spectrum of POPG MLVs.
    (C) Headgroup and glycerol backbone R-PDLF dipolar slices. The arrows indicate the splittings used to determine the C--H bond order parameters by using  $|S_{\rm{CH}}|=\Delta\nu/0.315/d_{\rm{CH}}$. The rigid coupling $d_{\rm{CH}}$ used was 22 kHz.
    (D) Experimental S-DROSS curves giving signs of the order parameters measured. Grey lines are a set of slices taken from a region of the spectrum without peaks, i.e. grey lines are noise profiles, to highlight the signal-to-noise ratio of the measured modulations. Note that the S-DROSS modulation for $g_3$ is very close to the noise level. In this case, we have confirmed that the order parameter sign of $g_3$ was negative by performing a measurement with less points in the indirect dimension, more scans and using a higher MAS frequency of 8 kHz. 
  }
\end{figure}

@@

\noindent
{\it Tiago M. Ferreira}
%% Please write description of your contribution here

>>>>

\begin{figure}[]
%  \centering
  \includegraphics[width=\textwidth]{./Figs/POPG_SI.pdf}
  \caption{\label{POPGspectra}
    Solid-state NMR spectroscopy for determining the C--H bond order parameters, $S_{\rm{CH}}$, in the POPG headgroup and glycerol backbone. (A) Chemical structure of POPG showing the labels used to identify different carbons.
    (B) Refocused INEPT $^{13}$C spectrum of POPG MLVs.
    (C) Headgroup and glycerol backbone R-PDLF dipolar slices. The arrows indicate the splittings used to determine the C--H bond order parameters by using  $|S_{\rm{CH}}|=\Delta\nu/0.315/d_{\rm{CH}}$. The rigid coupling $d_{\rm{CH}}$ used was 22 kHz.
    (D) Experimental S-DROSS curves giving signs of the order parameters measured. Grey lines are a set of slices taken from a region of the spectrum without peaks, i.e. grey lines are noise profiles, to highlight the signal-to-noise ratio of the measured modulations. Note that the S-DROSS modulation for $g_3$ is very close to the noise level. In this case, we have confirmed that the order parameter sign of $g_3$ was negative by performing a measurement with less points in the indirect dimension, more scans and using a higher MAS frequency of 8 kHz (not shown). 
  }
\end{figure}

@@

\noindent
{\it Tiago M. Ferreira}
performed and analysed the R-PDLF and S-DROSS experiments. Wrote p
